Reconstructing the Lensing Mass in the Universe \\ from Photometric Catalogue Data

### 2013-03-20 doc/paper-lcr.tex
new readme

High precision cosmological distance measurements towards individual objects
such as time delay gravitational lenses or type Ia supernovae are affected by
weak lensing perturbations by galaxies and groups along the line of sight. In
time delay gravitational lenses, ``external convergence,'' $\kappax$, can
dominate the uncertainty in the inferred distances and hence cosmological parameters.
 In this paper we attempt
to reconstruct $\kappax$, due to line of sight structure, using a simple halo
model.
%
We use mock catalogues from the Millennium Simulation, and calibrate and 
compare our reconstructed $\pr(\kappax)$ to ray-traced $\kappax$ ``truth''
values; taking into account realistic uncertainties on redshift and stellar
masses. \tom{We find that the reconstruction of $\kappax$ provides an improvement in
precision of $\sim$50\% over galaxy number counts.} 
%
We find that the lowest-$\kappax$ lines of sight have the best constrained 
$\pr(\kappax)$. In anticipation of future samples with thousands of lenses,
we find that selecting the third of the systems with the
highest precision $\kappax$ estimates gives a  sub-sample of unbiased time
delay distance measurements \phil{with (on average) just} 1\% uncertainty due
to line of sight external convergence effects. Photometric data alone are
sufficient to pre-select the best-constrained lines of sight, and can be done
before investment in lightcurve monitoring. 
%
\phil{Conversely, we show that selecting lines of sight
with high external shear could, with the reconstruction model presented here,
induce biases of up to 1\% in time delay distance.} \new{We find that a major potential source of systematic error is uncertainty in the high mass end of the stellar mass-halo mass relation; this could introduce $\sim$2\% biases on the time-delay distance if completely ignored.} We suggest areas for the
improvement of this general analysis framework (including more sophisticated
treatment of high mass structures) that should allow yet more accurate
cosmological inferences to be made.

@@

Since the mass-sheet degeneracy prevents any estimate of $\kappax$ from the 
strong lens modelling, additional information is required. Weak lensing measurements
can be used for rich lines of sight \citep{NakajimaEtal2009, FadelyEtal2009}, but 
for lines of sight with low galaxy density we must attempt to reconstruct the distribution
of mass along the line of sight. Attempts to reconstruct the mass distribution in strong
lens fields have focused on understanding the external shear which seems to be large in most strong lenses.
Surveys by \citet{Fassnacht+Lubin2002,AugerEtal2007,WilliamsEtal2006,MomchevaEtal2006,FassnachtEtal2006}
all found groups of galaxies hosting or near to known gravitational lenses.
Is generally found that lens galaxies, reside in overdense environments,
indistinguishable from those occupied by similarly massive galaxies \citep{Auger2008,TreuEtal2009}
\citet{WongEtal2011} estimated $\Pr(\gammax)$ given the data of \citet{WilliamsEtal2006}
and \citet{MomchevaEtal2006} but found significant discrepancy between the predicted shear
distribution and the external shear demanded by the strong lens model. 
\citeauthor{WongEtal2011} also found that both line of
sight structures and the group of galaxies in each lens plane contribute
significant proportions of the shear.

@@

% PHIL's REVIEWS OF THE LITERATURE
\comments{\citet{GunnarssonEtal2006} investigated a related PDF,  for the
magnification, using a galaxy halo model. Applying empirical galaxy
scaling relations both to simulate mock catalogues and then to reconstruct
the line of sight mass distribution. While they did not explore highly
over-dense lines of sight, or the impact of groups and clusters, they
found that under their simplifying assumptions, the dispersion in
apparent source brightness due to lensing magnification could be reduced
by a factor of two.}
%
\comments{\citet{WongEtal2011} estimated the PDF for the external shear,
$\Pr(\gammax|\data)$ from their survey data, running similar Monte Carlo
reconstructions of the mass in nine lens fields based on
\citeauthor{WilliamsEtal2006} and \citeauthor{MomchevaEtal2006}'s
photometric and spectroscopic measurements of galaxies close to the line
of sight. They then  compared the resulting predicted shear
distributions with the external shear demanded by the strong lens model.
Their reconstructions showed most of the shear to have been generated by
bright galaxies within 2~arcminutes of the lens, and that both line of
sight structures and the group of galaxies in each lens plane contribute
significant proportions of the shear. They found significant
discrepancies between the lens model shear and the Monte Carlo
predictions, but were unable to distinguish between the environment
modelling and the strong lens modelling as the cause of these
discrepancies.}
%
\comments{\citet{KarpenkaEtal2012} used a halo model to predict deterministically 
the magnification due to
galaxies along the line of sight to type Ia supernovae, and inferred the
parameters of scaling relations between light and mass in these galaxies
from hundreds of supernova lightcone simultaneously. Following
\citet{JonssonEtal2010}, they subtract off the mean convergence to ensure that
the universal mass budget is balanced, and compare models where the halos are
all have either truncated singular isothermal profiles, or 
NFW profiles. Both groups were able to 
detect lensing effects in the supernova data this way.}

@@

\phil{However, if the conversion between stellar mass and halo mass is very
uncertain, $\pr(\kappah|\data)$ is shifted relative to what it would
have been given perfect knowledge of the halo masses.  This is because the
conversion from stellar mass to halo mass and into $\kappah$ is highly
asymmetric: a long tail of high halo masses gives rise to a tendency to
overestimate $\kappah$. If this shift is ignored, the resulting
$\Pr(\kappax|\data)$ will be systematically biased towards high values of
$\kappax$. Instead, we need the  distribution of $\kappax$ from all
calibration lines of sight that have a $\pr(\kappah|\data)$ that is identical
to the $\pr(\kappah|\data)$ for the real line of sight {\it given the same
data quality}; however, we found this approach unfeasible  given our finite
number of calibration lines of sight. A working compromise is to use 
the median of the $\pr(\kappah|\data)$ distributions in the calibration.}

@@

While a fully photometric reconstruction provides useful constraints on
$\pr(\kappax|\data)$, targeted spectroscopy can provide additional constraints
on the masses and redshifts of halos whose $\kappah$ contributions have the
largest absolute uncertainty. Obtaining spectra of bright ($i<22$) objects is
relatively fast with large telescopes: however, we find that if spectroscopic
redshifts were known for all $i<22$ galaxies in our fields the reconstruction
improves only slightly over the purely photometric reconstruction,  although
the improvement can depend strongly on the details of the particular line of
sight. Obtaining spectra for fainter objects would be correspondingly more
expensive, but if spectroscopic redshifts could be obtained for all $i<23$
galaxies (as part of a futuristic baryon acoustic oscillation survey, for
example) and all $i<24$ galaxies within 1 arcminute of the line of sight, then
we find that the $\pr(\kappax|\data)$ would be almost as precise as that from
having complete spectroscopic coverage (\Fref{fig:reconwidths}). If any object is
extremely close to the lines of sight our approximation of weakly lensing
mass-sheets will break down; also, neglecting baryonic effects will also be a poor
approximation; a spectrum will be needed
to adequately model systems with very well alligned pertrubers.
Consistent with our previous findings, the lowest $\kappax$ lines of
sight have the most constrained $\kappax$ PDFs.

@@

We first consider a purely random selection of lines of sight. With the purely
photometric reconstruction, there is no evidence of bias, even after combining
20 lines of sight. \tom{This result is a sanity check: if we had chosen lines
of sight with identical $\kappah^{\rm med}$ rather than $\kappah^{\rm
med}\pm0.003$, randomly selected lines of sight would have zero bias by
construction}. If lines of sight hosting time delay lenses are truely random, 
our method allows $\kappax$ to be reconstructed without inducing a bias (under
the basic assumptions that the universe is like the calibration simulation,
and the correct stellar-mass to halo-mass relation has been used).

@@

Throughout this work we have assumed that the universe's halos are populated
with galaxies whose stellar masses are determined purely by the
\citet{BehrooziEtal2010} Stellar Mass--Halo Mass relation, which we then use
in our reconstruction. In practice, the true Stellar Mass--Halo Mass relation
may well be different to the one we assume in our inference, and if it is, 
a systematic error could be incurred. It is hard to test the size of this sytematic error, since we do not know how much the real universe differs from the chosen Stellar Mass--Halo Mass relation. As wider and deeper surveys are conducted more data will become available with which to construct the Stellar Mass--Halo Mass relation; this should drive the infered Stellar Mass--Halo Mass relation closer to the truth. We are only interested in testing the effect of changing the Stellar Mass--Halo Mass relation in a way that is consistant with observational constraints; improving the observational contraints on the Stellar Mass--Halo Mass relation will decrease the the potential size of the systematic error on reconstructed $\kappax$ induced by assuming a specfic Stellar Mass--Halo Mass relation.

To estimate the potential size of this systematic error, we repeat the
analysis of the previous section, still using the  the
Behroozi et al. relation to generate the stellar masses of our
calibration lines of sight and hence carry out the inference, but now using
simulated catalog datasets that were generated from the stellar mass--halo
mass relation of Moster et al.

@@

Applying our Behroozi--based reconstruction to lines of sight with Moster
stellar masses results in systematic overestimates of $\kappax$. In
\Fref{fig:SHAMbias} we show this bias emerging after combining several lines
of sight. With a purely photometric reconstruction there is a typical
systematic bias of $\sim 0.025$ on the reconstructed convergence. This can be
shrunk to $\sim 0.01$ if only the low $\kappax$ lines of sight are used;
however for the high shear lines of sight the bias is $\sim 0.04$. It is not
too suprising that the low $\kappax$ lines of sight are least affected by
changes in the stellar mass--halo mass relation. Low $\kappax$ lines of sight
are relatively empty, their $\kappah$ values are small, and they do not depend
as strongly on the stellar mass--halo mass relation. In contrast, the high
shear lines of sight have significantly overestimated $\kappax$ values, since
they tend to lie close to massive halos -- the regime where the Moster
and Behroozi relations are most different. Interestingly, overestimating the
$\kappah$ values of high shear lines of sight pushes them into the region
where the $\kappah$ to $\kappax$ calibration is least certain; this 
significantly decreases the precision of the reconstructed $\kappax$.

Despite these systematic errors, we find that the photometric reconstruction
is still sufficient to choose the best lines of sight for spectroscopic
follow-up. With targeted spectroscopy the systematic error decreases to $\sim
0.014$ for the ensemble, $\sim 0.005$ for the low kappa sample and $\sim
0.018$ for the high shear sample. These results provides further motivation for
prioritizing the lenses that reside on the underdense lines of sight.

@@

The reduction of $\pr(\kappah|\data)$ to just its median value, before using
it to look up the appropriate $\pr(\kappax)$ from the simulated sightline
ensemble, is reminiscent of the procedure followed by \citet{SuyuEtal2010},
and Greene et al (submitted). The reconstruction method presented here can be
seen as the limiting case of the weightings explored by Greene et al: rather
than using weighted number counts in an aperture, we treat each galaxy
individually, and predict $\kappa_{\rm h,obs}^{\rm med}$ for use in their
place. Given photometry alone, our reconstruction represents a $\sim$50\% improvement of
the precision compared the number counts used in \citet{SuyuEtal2010}. Greene et al.
made important progress for the most over-dense lines of sight; our
reconstructions are $\sim$30\% more precise than those of Greene et al.
The use of relative overdensities by Suyu et al. and Greene et al. may decrease 
their sensitivity to the choice of calibration simulation; this work's use of
absolute convergence may be less robust to changes in the calibration simulation.

@@

In this work, we have used  the \MS as a calibration tool. If the real
Universe is not like the \MS, then this calibration will be incorrect.
Repeating this study using a different simulation to make the test catalogues
would allow us to quantify the sensitivity of our results to the simulation
used. Similarly the use of a different semi-analytic model to paint galaxies
onto halos would enable similar exploration of these systematic errors. 
\citet{SuyuEtal2010}
used the relative over-density to mitigate the effect of simulatioan and
simulation, but it does not completely remove the dependence on simulation.
\new{We have tested the effect of using a different stellar mass--halo mass relation
and found that this can induce significant systematic biases if the true relation is unknown.} Future work should include
investigating the robustness of the reconstruction to these systematic errors \new{and develope proscriptions that mitigate against them}

@@

\item Despite our model's simplicity, its reconstructed $\kappah$ values are
good tracers of $\kappax$. $\kappah$ is biased due to our ignorance of voids,
groups and clusters, and the unseen mass in small halos and filaments, but we
find that this can be calibrated out using the Millenium Simulation
catalogues. We found that with perfect knowledge of every halo's mass and
redshift,  calibrated reconstruction of a typical line of sight  gives an
unbiased estimate of $\kappax$ that is not perfect, but is $1.8$ 
times more precise than the global
$\pr(\kappax)$. This factor quantifies the limit to which the halo model can
represent the external convergence due to line of sight mass structure.

@@

\item \new{Reconstructing a line of sight with an incorrect stellar mass--halo mass relation can introduce systematic errors on the inferrred time-delay distance at the percent level. This error can be reduced by tightening the observational limits on the stellar mass--halo mass relation at the high mass end.}

>>>>

High precision cosmological distance measurements towards individual objects
such as time delay gravitational lenses or type Ia supernovae are affected by
weak lensing perturbations by galaxies and groups along the line of sight. In
time delay gravitational lenses, ``external convergence,'' $\kappax$, can
dominate the uncertainty in the inferred distances and hence cosmological parameters.
 In this paper we attempt
to reconstruct $\kappax$, due to line of sight structure, using a simple halo
model.
%
We use mock catalogues from the Millennium Simulation, and calibrate and 
compare our reconstructed $\pr(\kappax)$ to ray-traced $\kappax$ ``truth''
values; taking into account realistic uncertainties on redshift and stellar
masses. \tom{We find that the reconstruction of $\kappax$ provides an improvement in
precision of $\sim$50\% over galaxy number counts.} 
%
We find that the lowest-$\kappax$ lines of sight have the best constrained 
$\pr(\kappax)$. In anticipation of future samples with thousands of lenses,
we find that selecting the third of the systems with the
highest precision $\kappax$ estimates gives a  sub-sample of unbiased time
delay distance measurements \phil{with (on average) just} 1\% uncertainty due
to line of sight external convergence effects. Photometric data alone are
sufficient to pre-select the best-constrained lines of sight, and can be done
before investment in light-curve monitoring. 
%
\phil{Conversely, we show that selecting lines of sight
with high external shear could, with the reconstruction model presented here,
induce biases of up to 1\% in time delay distance.} \new{We find that a major potential source of systematic error is uncertainty in the high mass end of the stellar mass-halo mass relation; this could introduce $\sim$2\% biases on the time-delay distance if completely ignored.} We suggest areas for the
improvement of this general analysis framework (including more sophisticated
treatment of high mass structures) that should allow yet more accurate
cosmological inferences to be made.

@@

Since the mass-sheet degeneracy prevents any estimate of $\kappax$ from the 
strong lens modelling, additional information is required. Weak lensing measurements
can be used for rich lines of sight \citep{NakajimaEtal2009, FadelyEtal2009}, but 
for lines of sight with low galaxy density we must attempt to reconstruct the distribution
of mass along the line of sight. Attempts to reconstruct the mass distribution in strong
lens fields have focused on understanding the external shear which seems to be large in most strong lenses.
Surveys by \citet{Fassnacht+Lubin2002,AugerEtal2007,WilliamsEtal2006,MomchevaEtal2006,FassnachtEtal2006}
all found groups of galaxies hosting or near to known gravitational lenses.
Is generally found that lens galaxies, reside in over-dense environments,
indistinguishable from those occupied by similarly massive galaxies \citep{Auger2008,TreuEtal2009}
\citet{WongEtal2011} estimated $\Pr(\gammax)$ given the data of \citet{WilliamsEtal2006}
and \citet{MomchevaEtal2006} but found significant discrepancy between the predicted shear
distribution and the external shear demanded by the strong lens model. 
\citeauthor{WongEtal2011} also found that both line of
sight structures and the group of galaxies in each lens plane contribute
significant proportions of the shear.

@@

% PHIL's REVIEWS OF THE LITERATURE
\comments{\citet{GunnarssonEtal2006} investigated a related PDF,  for the
magnification, using a galaxy halo model. Applying empirical galaxy
scaling relations both to simulate mock catalogues and then to reconstruct
the line of sight mass distribution. While they did not explore highly
over-dense lines of sight, or the impact of groups and clusters, they
found that under their simplifying assumptions, the dispersion in
apparent source brightness due to lensing magnification could be reduced
by a factor of two.}
%
\comments{\citet{WongEtal2011} estimated the PDF for the external shear,
$\Pr(\gammax|\data)$ from their survey data, running similar Monte Carlo
reconstructions of the mass in nine lens fields based on
\citeauthor{WilliamsEtal2006} and \citeauthor{MomchevaEtal2006}'s
photometric and spectroscopic measurements of galaxies close to the line
of sight. They then  compared the resulting predicted shear
distributions with the external shear demanded by the strong lens model.
Their reconstructions showed most of the shear to have been generated by
bright galaxies within 2~arcminutes of the lens, and that both line of
sight structures and the group of galaxies in each lens plane contribute
significant proportions of the shear. They found significant
discrepancies between the lens model shear and the Monte Carlo
predictions, but were unable to distinguish between the environment
modelling and the strong lens modelling as the cause of these
discrepancies.}
%
\comments{\citet{KarpenkaEtal2012} used a halo model to predict deterministically 
the magnification due to
galaxies along the line of sight to type Ia supernovae, and inferred the
parameters of scaling relations between light and mass in these galaxies
from hundreds of supernova light-cone simultaneously. Following
\citet{JonssonEtal2010}, they subtract off the mean convergence to ensure that
the universal mass budget is balanced, and compare models where the halos are
all have either truncated singular isothermal profiles, or 
NFW profiles. Both groups were able to 
detect lensing effects in the supernova data this way.}

@@

\phil{However, if the conversion between stellar mass and halo mass is very
uncertain, $\pr(\kappah|\data)$ is shifted relative to what it would
have been given perfect knowledge of the halo masses.  This is because the
conversion from stellar mass to halo mass and into $\kappah$ is highly
asymmetric: a long tail of high halo masses gives rise to a tendency to
overestimate $\kappah$. If this shift is ignored, the resulting
$\Pr(\kappax|\data)$ will be systematically biased towards high values of
$\kappax$. Instead, we need the  distribution of $\kappax$ from all
calibration lines of sight that have a $\pr(\kappah|\data)$ that is identical
to the $\pr(\kappah|\data)$ for the real line of sight {\it given the same
data quality}; however, we found this approach infeasible  given our finite
number of calibration lines of sight. A working compromise is to use 
the median of the $\pr(\kappah|\data)$ distributions in the calibration.}

@@

While a fully photometric reconstruction provides useful constraints on
$\pr(\kappax|\data)$, targeted spectroscopy can provide additional constraints
on the masses and redshifts of halos whose $\kappah$ contributions have the
largest absolute uncertainty. Obtaining spectra of bright ($i<22$) objects is
relatively fast with large telescopes: however, we find that if spectroscopic
redshifts were known for all $i<22$ galaxies in our fields the reconstruction
improves only slightly over the purely photometric reconstruction,  although
the improvement can depend strongly on the details of the particular line of
sight. Obtaining spectra for fainter objects would be correspondingly more
expensive, but if spectroscopic redshifts could be obtained for all $i<23$
galaxies (as part of a futuristic baryon acoustic oscillation survey, for
example) and all $i<24$ galaxies within 1 arcminute of the line of sight, then
we find that the $\pr(\kappax|\data)$ would be almost as precise as that from
having complete spectroscopic coverage (\Fref{fig:reconwidths}). If any object is
extremely close to the lines of sight our approximation of weakly lensing
mass-sheets will break down; also, neglecting baryonic effects will also be a poor
approximation; a spectrum will be needed
to adequately model systems with very well aligned pertrubers.
Consistent with our previous findings, the lowest $\kappax$ lines of
sight have the most constrained $\kappax$ PDFs.

@@

We first consider a purely random selection of lines of sight. With the purely
photometric reconstruction, there is no evidence of bias, even after combining
20 lines of sight. \tom{This result is a sanity check: if we had chosen lines
of sight with identical $\kappah^{\rm med}$ rather than $\kappah^{\rm
med}\pm0.003$, randomly selected lines of sight would have zero bias by
construction}. If lines of sight hosting time delay lenses are truly random, 
our method allows $\kappax$ to be reconstructed without inducing a bias (under
the basic assumptions that the universe is like the calibration simulation,
and the correct stellar-mass to halo-mass relation has been used).

@@

Throughout this work we have assumed that the universe's halos are populated
with galaxies whose stellar masses are determined purely by the
\citet{BehrooziEtal2010} Stellar Mass--Halo Mass relation, which we then use
in our reconstruction. In practice, the true Stellar Mass--Halo Mass relation
may well be different to the one we assume in our inference, and if it is, 
a systematic error could be incurred. It is hard to test the size of this systematic error, since we do not know how much the real universe differs from the chosen Stellar Mass--Halo Mass relation. As wider and deeper surveys are conducted more data will become available with which to construct the Stellar Mass--Halo Mass relation; this should drive the inferred Stellar Mass--Halo Mass relation closer to the truth. We are only interested in testing the effect of changing the Stellar Mass--Halo Mass relation in a way that is consistent with observational constraints; improving the observational constraints on the Stellar Mass--Halo Mass relation will decrease the the potential size of the systematic error on reconstructed $\kappax$ induced by assuming a specific Stellar Mass--Halo Mass relation.

To estimate the potential size of this systematic error, we repeat the
analysis of the previous section, still using the  the
Behroozi et al. relation to generate the stellar masses of our
calibration lines of sight and hence carry out the inference, but now using
simulated catalogue datasets that were generated from the stellar mass--halo
mass relation of Moster et al.

@@

Applying our Behroozi--based reconstruction to lines of sight with Moster
stellar masses results in systematic overestimates of $\kappax$. In
\Fref{fig:SHAMbias} we show this bias emerging after combining several lines
of sight. With a purely photometric reconstruction there is a typical
systematic bias of $\sim 0.025$ on the reconstructed convergence. This can be
shrunk to $\sim 0.01$ if only the low $\kappax$ lines of sight are used;
however for the high shear lines of sight the bias is $\sim 0.04$. It is not
too surprising that the low $\kappax$ lines of sight are least affected by
changes in the stellar mass--halo mass relation. Low $\kappax$ lines of sight
are relatively empty, their $\kappah$ values are small, and they do not depend
as strongly on the stellar mass--halo mass relation. In contrast, the high
shear lines of sight have significantly overestimated $\kappax$ values, since
they tend to lie close to massive halos -- the regime where the Moster
and Behroozi relations are most different. Interestingly, overestimating the
$\kappah$ values of high shear lines of sight pushes them into the region
where the $\kappah$ to $\kappax$ calibration is least certain; this 
significantly decreases the precision of the reconstructed $\kappax$.

Despite these systematic errors, we find that the photometric reconstruction
is still sufficient to choose the best lines of sight for spectroscopic
follow-up. With targeted spectroscopy the systematic error decreases to $\sim
0.014$ for the ensemble, $\sim 0.005$ for the low kappa sample and $\sim
0.018$ for the high shear sample. These results provides further motivation for
prioritizing the lenses that reside on the under-dense lines of sight.

@@

The reduction of $\pr(\kappah|\data)$ to just its median value, before using
it to look up the appropriate $\pr(\kappax)$ from the simulated sightline
ensemble, is reminiscent of the procedure followed by \citet{SuyuEtal2010},
and Greene et al (submitted). The reconstruction method presented here can be
seen as the limiting case of the weightings explored by Greene et al: rather
than using weighted number counts in an aperture, we treat each galaxy
individually, and predict $\kappa_{\rm h,obs}^{\rm med}$ for use in their
place. Given photometry alone, our reconstruction represents a $\sim$50\% improvement of
the precision compared the number counts used in \citet{SuyuEtal2010}. Greene et al.
made important progress for the most over-dense lines of sight; our
reconstructions are $\sim$30\% more precise than those of Greene et al.
The use of relative over-densities by Suyu et al. and Greene et al. may decrease 
their sensitivity to the choice of calibration simulation; this work's use of
absolute convergence may be less robust to changes in the calibration simulation.

@@

In this work, we have used  the \MS as a calibration tool. If the real
Universe is not like the \MS, then this calibration will be incorrect.
Repeating this study using a different simulation to make the test catalogues
would allow us to quantify the sensitivity of our results to the simulation
used. Similarly the use of a different semi-analytic model to paint galaxies
onto halos would enable similar exploration of these systematic errors. 
\citet{SuyuEtal2010}
used the relative over-density to mitigate the effect of simulation and
simulation, but it does not completely remove the dependence on simulation.
\new{We have tested the effect of using a different stellar mass--halo mass relation
and found that this can induce significant systematic biases if the true relation is unknown.} Future work should include
investigating the robustness of the reconstruction to these systematic errors \new{and develop prescriptions that mitigate against them}

@@

\item Despite our model's simplicity, its reconstructed $\kappah$ values are
good tracers of $\kappax$. $\kappah$ is biased due to our ignorance of voids,
groups and clusters, and the unseen mass in small halos and filaments, but we
find that this can be calibrated out using the Millennium Simulation
catalogues. We found that with perfect knowledge of every halo's mass and
redshift,  calibrated reconstruction of a typical line of sight  gives an
unbiased estimate of $\kappax$ that is not perfect, but is $1.8$ 
times more precise than the global
$\pr(\kappax)$. This factor quantifies the limit to which the halo model can
represent the external convergence due to line of sight mass structure.

@@

\item \new{Reconstructing a line of sight with an incorrect stellar mass--halo mass relation can introduce systematic errors on the inferred time-delay distance at the percent level. This error can be reduced by tightening the observational limits on the stellar mass--halo mass relation at the high mass end.}
